The \emph{FrobeniusThresholds} package for \emph{Macaulay2}

### 2019-06-11 Fsing/FThresholdsPaper/FThresholds.tex

One natural direction of development would be to better incorporate the test ideals $\tau(I^t)$ when computing $F$-thresholds when the ideal $I$ is nonprincipal.
The theoretical foundation for computing such test ideals has already been laid out in \cite{SchwedeTuckerTestIdealsOfNonPrincipal}, but such an update to the \emph{FrobeniusThresholds} package would require the  \emph{TestIdeals} package to be updated first.

>>>>

One natural direction of development would be to better incorporate the test ideals $\tau(I^t)$ when computing $F$-thresholds in the case where the ideal $I$ is nonprincipal.
The theoretical foundation for computing such test ideals has already largely been worked out in \cite{SchwedeTuckerTestIdealsOfNonPrincipal}, but such an update to the \emph{FrobeniusThresholds} package would require the  \emph{TestIdeals} package to be updated first.
